A new type of automated prover based on category theory

### 2022-08-08 paper.tex
improve typesetting

\newcommand{\mathsym}[1]{{}}
\newcommand{\unicode}[1]{{}}

@@

Mainly developed in the twentieth century by the contribution of MacLane and Eilenberg with the purpose to investigate algebra topology, the category theory is a fast-evolving aspect of modern mathematics. In just a few decades, the category theory has become the standard and formal language of homology algebra and algebraic geometry and has gained a lot of meaningful achievements, for instance the Yoneda{'}s Lemma and Braid categories, which serves as a neat explanation for the Yang-Baxter Equation (YBE). Moreover, the category theory{'}s main idea, which is to put mathematical structures into categories satisfies the worldview of the Bourbaki school.

In this paper I will present a new approach of automated proving using knowledge of the category, as well as its theoretical foundation, and will provide a new algorithm which can prove mathematical statements comprehensively. Additionally, an executable program and its implementation process will be describe later.

\textit{ Structure of the paper.}\\
The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols I select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.f

@@

\pmb{ Axiom.} The Selection Axiom.

Let \(X\) be a set and each of \(X\){'}s elements not empty, then there exists function \(g:X\to \cup X\) making \(\forall x\in X,g(x)\in x\), naming \(g(x)\) as the selection function.

@@

\pmb{ Theorem. }The Zermelo{'}s Well-Ordering Theorem.\cite{1}

@@

Then, since \(S\) is a set, a minimized \(\theta\) can be chosen making \(a_{\theta }=\mho , S=\left\{\left.a_{\beta }\right|\beta <\theta \right\}\) and significantly there exists a bijection between \(S\) and \(\theta =\{\beta |\beta <\theta \}\). Following the definition, there obviously exists a well-ordering on \(S\).
\begin{flushright}
	$\blacksquare $
\end{flushright}

@@

\pmb{ Definition.} A \textbf{ bracket} \(\beta\) is defined as a set of ordered pairs in the form of below:

@@

\[\beta =\{(j,\mathcal{N})\}\cup \left\{(i,x)\left|i\in \text{On}_{\geq 1}\right., x\in \text{Sym}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\right\},\forall
t\in \beta ,j\in \text{On}_{\left[1,t_{\ell }\right]}\]

@@

\pmb{ Definition.} Two bracket \(\alpha\) and \(\beta\), are thought to be \textbf{ isomorphic} (noted as \(\alpha \simeq \beta\)) if they satisfy the following restrictions:

First, \(|\alpha |=|\beta |\) indicating the two brackets have same cardinal numbers. Second, all right elements sorted in the order defined by the sort of the left pair elements, correspondingly, are either same or symbols with the same type. Otherwise, the two brackets are \textbf{ not isomorphic}, noted as \(\alpha \not{\simeq}\beta\).

@@

\pmb{ Definition.} A \textbf{ notation} \(\mathcal{N}\) is defined as an object in \(\text{Not}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). The \(\text{Ob}(\text{Not}(\mathcal{C}))\) set can be mapped to \(\text{On}_{\geq 0}\) class, indicating the number of parameters that a notation take. In which,

@@

In that case if \(n=0\) then we say \(\mathcal{N}\) is a \textbf{ type} and if \(n>0\) then \(\mathcal{N}\) is an \textbf{ operator}. For instance, obviously, \(\mathit{p}(+)=2\) and \(\mathit{p}(\neg )=1\). A notation\(\mathcal{N}\) is called \textbf{ finite} if \(\mathit{p}(\mathcal{N})<\omega\), and otherwise \(\mathcal{N}\) can have infinite number of symbols as parameters, when the notation is called to be \textbf{ infinite}.

@@

\pmb{ Definition.} A \textbf{ symbol} \(\mathcal{S}\) is defined as an object in \(\text{Sym}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). There exists a functor from \(\text{Sym}(\mathcal{C})\) to \(\text{Not}(\mathcal{C})\):

@@

\[\epsilon :\alpha \equiv \beta\]

@@

\pmb{ Definition.} A notation \(\mathcal{N}\) is called being \textbf{ inherited} from notation \(\mathcal{M}\) (or we say \(\mathcal{N}\) is\textbf{  a kind of} \(\mathcal{M}\)) when there exists such morphism between the two in \(\text{Not}(\mathcal{C})\):

@@

It is obviously without any ambiguity that \(\forall \mathcal{M},\mathcal{N}\in \text{Not}(\mathcal{C}),\left|\text{Hom}_{\mathcal{C}}(\mathcal{M},\mathcal{N})\right|\in \{0,1\}\). Moreover, if \(\mathcal{N}\) is a kind of \(\mathcal{M}\) then \(\mathit{p}(\mathcal{N})\geq \mathit{p}(\mathcal{M})\). For simplicity, \(\mathcal{N}\) is inherited from \(\mathcal{M}\) can be annotated as \(\mathcal{N}\triangleleft |\mathcal{M}\).

@@

\pmb{ Example.} Using the structure provided by Bracket, Notation and Symbol to construct the example formula below, with meta category \(\mathcal{C}_1\).

@@

\pmb{ Definition.} A micro-statement is a defined as an object in \(\text{Bra}(\mathcal{C})\) whose notation \(\mathcal{N}\) has \(\mathit{p}(\mathcal{N})=2\) and can be evaluated into a Boolean.

It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the \textbf{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the \textbf{ Micro-Statement }sub category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).

@@

\pmb{ Definition.} An evaluation is a morphism from \(\text{Mic}(\mathcal{C})\) to a Boolean algebra \(\mathcal{B}\) with the form below.

@@

The Boolean value \(\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})\in \{0,1\}\) is called the \textbf{ evaluation result} of micro-statement. If for bracket \(\mathit{m}\) exists a morphism to \(\mathcal{B}\) that satisfies the definition of evaluation, then we say that \(\mathit{m}\) is \textbf{ evaluatable}. That is, if it satisfies the first restriction of being a micro-statement as well, it is a micro-statement.

@@

The discussion below calls the \(\text{Mic}(\mathcal{C})\) category the \textbf{ micro-statement pool}, or \textbf{ pool} for short. The morphisms inside the micro-statements pool are declared for representation of implication relationships. It is obvious are elementary that,

@@

\pmb{ Definition.} A \textbf{ derivation} is a set of ordered pairs of ordinals and categories in the form below.

@@

For simplicity of expression, we use notation \(\mathcal{M}_i\) to represent the right pair element in $\mathcal{D}$ { }whose left companion is \(i\).

@@

\pmb{ Definition.} A \textbf{ step of derivation} is a map existed on the derivation set \(\mathcal{D}\), mapping from a pair to another, whose ordinal increases by \(1\). This map is annotated using script word \(\mathit{s}\mathit{t}\mathit{e}\mathit{p}\). The form is shown below:

@@

\[\mathcal{M}_{i+1}=\mathcal{F}_i\mathcal{M}_i\]

@@

\pmb{ Definition.} A derivation set is thought to be \textbf{ successful} when the condition below is satisfied when the condition below is true:

@@

On the other hand, a derivation set is thought to be \textbf{ impossible} when there does not exist such a \(n\in [0,\omega )\) that makes the requirement set a subset of the object set of the targeted micro-statement pool.

@@

\pmb{ Definition. }A \textbf{ reflection functor} \(\mathcal{K}\) is defined as an functor object in a functor category \(\mathcal{R}\mathit{e}\mathit{f}\), who maps between two micro-statement pools. Because of the Zermelo{'}s Well-Ordering Theorem we mentioned in the Preliminary section, \(\text{Ob}(\mathcal{R}\mathit{e}\mathit{f})\) can be put into well-order, with ordinal \(i\). All of the reflection functors forms a functor category \(\mathcal{Q}\), called the \textbf{ reflection knowledge base}, or for short the \textbf{ knowledge base}. The detailed explanation and description, including the utilization of and morphisms inside the knowledge base, will be discussed later in this section of the paper. We annotate each of the functor positioned at location \(i\) with \(\mathcal{K}_i\).

@@

\[\sigma =T(\mathcal{K})_{\ell }\]
\[\tau =T(\mathcal{K})_{\mathit{r}}\]

@@

\pmb{ Definition.} The process of isomorphism inspection is declared as below. The stuff that the isomorphism inspection process manipulates is a micro-statement \(\mu \in \mathcal{M}_i\), a special evaluatable sort of bracket. The definition of bracket being isomorphic can be found in the second section. Explicitly, the inspection process is to construct a new set called the \textbf{ transformation source}, noted as \(\text{Ts}\) using the equation below.

\[\text{Ts}\text{:=}\left\{t\in \mathcal{M}_i|t\simeq T(\mathcal{K})_{\ell }\right\}\]

@@

\pmb{ Definition.} A \textbf{ transformation map} is a one-one map defined between the list of symbol and sub-brackets of the two brackets \(\alpha\) and \(\beta\) where,

@@

\[\mathcal{M}_{i+1}=\mathcal{M}_i\cup \mathcal{M}'\]

@@

\pmb{ Definition. }The \textbf{ initial map }is the original state of knowledge base \(\mathcal{Q}\) when \(\mathcal{Q}\) is created. Initially, after the reflection functors are sorted, while discussions around this take place before, they forms a circular with connection of morphisms. That is, for \(N=|\text{Ob}(\mathcal{Q})|\),

@@

A morphism in this category means that if the reflection functor on its start is executed just now, then the target functor will be executed next time. That is, to be more specific, if a functor in \(\mathcal{Q}\) has no morphisms targeting it, then it will be never executed unless it is configured as the beginning functor (location \(0\)) manually. Moreover, if a functor has more than one morphisms starting from it, then we call this functor \textbf{ extroverted}. Otherwise, if a functor has more than one morphisms targeting it, it is \textbf{ introverted}. If one has only two morphisms connected, one in and one out, thus it is\textbf{  ordinary}. The process of determining the next functor of a extroverted functor will be discussed below.

@@

\pmb{ Definition. }A recursive functor \(\mathcal{F}_i\) is a functor that applies to pool \(\mathcal{M}_i\) and evolves it into \(\mathcal{M}_{i+1}\). The process of determining which \(\mathcal{K}_w\) is \textbf{ selected} after former reflection functor \(\mathcal{K}_j\) generally works on the knowledge base \(\mathcal{Q}\), right starting from the initial map. If this is the first time for the recursive functor to execute, then \(\mathcal{K}_0\) is selected. If \(\mathcal{F}_i\) encounters with an introverted or ordinary functor \(\mathcal{K}_j\) then significantly,

@@

It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \textbf{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm I learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{6} before.

@@

\pmb{ Definition.} The process of knowledge reinforcement is done after a finishing a proof. The first step of this reinforcement is to add numbers of utilization of the corresponding morphism of copies of morphisms into the knowledge base, increasing the weight of connections between the reflection functors. When next time a proof is issued, the modified knowledge base is \textbf{ loaded} into instance and act as the modified initial situation.

The second step of this sort of reinforcement is called \textbf{ reduction}, which is based on the Ebbinghaus{'}s forgetful curve{'}s numerical fit function. The exact form of the function expression can be found in the Preliminary section. Specifically, the number of morphisms is decreased following the forgetful equation, changing into the nearest integer number. To be more explicit, the Ebbinghaus-reduced decimal is stored separately from the knowledge base and the exact and accurate representation for this is omitted in the paper.

A situation after some reinforcements may be the one demonstrated in the figure below.

@@

		\path[commutative diagrams/.cd, every arrow, every label, dashed]
		(K3) edge node {$K_3$} (Kn)
		(Kn) edge node {$k_N$} (K0);
	\end{tikzpicture}
	\caption{An example map after several reinforcements.}
\end{figure}

@@

Currently I have developed a computer program called DefQed that implements the algorithm and it is open-sourced with BSD 3-Clause {``}New{''} or {``}Revised{''} License on GitHub. The source code of the latest version can be accessed at \cite{7} It should be noted that the version is very early and some aspects of the algorithm I presented in the paper is not implemented.

@@

\bibliographystyle{alpha}
\bibliography{document}
\end{document}

>>>>

\newcommand{\mathsym}[1]{{}}
\newcommand{\unicode}[1]{{}}
\newtheorem{theorem}{Theorem}
\newtheorem{axiom}{Axiom}
\newtheorem{definition}{Definition}
%% \newtheorem{example}{Example}

@@

Mainly developed in the twentieth century by the contribution of MacLane and Eilenberg with the purpose to investigate algebra topology, the category theory is a fast-evolving aspect of modern mathematics. In just a few decades, the category theory has become the standard and formal language of homology algebra and algebraic geometry and has gained a lot of meaningful achievements, for instance the Yoneda{'}s Lemma and Braid categories, which serves as a neat explanation for the Yang-Baxter Equation (YBE) \cite{1}. Moreover, the category theory{'}s main idea, which is to put mathematical structures into categories satisfies the worldview of the Bourbaki school.

In this paper I will present a new approach of automated proving using knowledge of the category, as well as its theoretical foundation, and will provide a new algorithm which can prove mathematical statements comprehensively. Additionally, an executable program and its implementation process will be described later.

\textit{ Structure of the paper.}\\
The paper mainly consists of seven sections. The Introduction section demonstrates the background of the research and fundamental opinions around it. The Preliminaries section, made up of two subsections, claims to minimized pre-knowledge required to understand the paper and the symbols I select to use. The third section defines a set of mathematical structures that will be used by the algorithm. The forth section explains the detailed workflow procedures of the algorithm. The next section claims the conclusions of the research and the to-do improvements in the future. Finally the Acknowledgments section expresses my gratitude to the help and the References section claims the referential resources used while conducting the project.

@@

%%\pmb{ Axiom.} The Selection Axiom.
\begin{axiom}
	The Selection Axiom.

	Let \(X\) be a set and each of \(X\){'}s elements not empty, then there exists function \(g:X\to \cup X\) making \(\forall x\in X,g(x)\in x\), naming \(g(x)\) as the selection function.
\end{axiom}

@@

%%\pmb{ Theorem. }
\begin{theorem}
	The Zermelo{'}s Well-Ordering Theorem.\cite{1}

@@

	Then, since \(S\) is a set, a minimized \(\theta\) can be chosen making \(a_{\theta }=\mho , S=\left\{\left.a_{\beta }\right|\beta <\theta \right\}\) and significantly there exists a bijection between \(S\) and \(\theta =\{\beta |\beta <\theta \}\). Following the definition, there obviously exists a well-ordering on \(S\).
	\begin{flushright}
		$\blacksquare $
	\end{flushright}
\end{theorem}

@@

%% \pmb{ Definition.} 
\begin{definition}
	A \textbf{ bracket} \(\beta\) is defined as a set of ordered pairs in the form of below:

@@

	\[\beta =\{(j,\mathcal{N})\}\cup \left\{(i,x)\left|i\in \text{On}_{\geq 1}\right., x\in \text{Sym}(\mathcal{C})\cup \text{Bra}(\mathcal{C})\right\},\forall
	t\in \beta ,j\in \text{On}_{\left[1,t_{\ell }\right]}\]
\end{definition}

@@

%% \pmb{ Definition.} 
\begin{definition}
	Two bracket \(\alpha\) and \(\beta\), are thought to be \textbf{ isomorphic} (noted as \(\alpha \simeq \beta\)) if they satisfy the following restrictions:

	First, \(|\alpha |=|\beta |\) indicating the two brackets have same cardinal numbers. Second, all right elements sorted in the order defined by the sort of the left pair elements, correspondingly, are either same or symbols with the same type. Otherwise, the two brackets are \textbf{ not isomorphic}, noted as \(\alpha \not{\simeq}\beta\).
\end{definition}

@@

%% \pmb{ Definition.} 
\begin{definition}
	A \textbf{ notation} \(\mathcal{N}\) is defined as an object in \(\text{Not}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). The \(\text{Ob}(\text{Not}(\mathcal{C}))\) set can be mapped to \(\text{On}_{\geq 0}\) class, indicating the number of parameters that a notation take. In which,

@@

	In that case if \(n=0\) then we say \(\mathcal{N}\) is a \textbf{ type} and if \(n>0\) then \(\mathcal{N}\) is an \textbf{ operator}. For instance, obviously, \(\mathit{p}(+)=2\) and \(\mathit{p}(\neg )=1\). A notation\(\mathcal{N}\) is called \textbf{ finite} if \(\mathit{p}(\mathcal{N})<\omega\), and otherwise \(\mathcal{N}\) can have infinite number of symbols as parameters, when the notation is called to be \textbf{ infinite}.
\end{definition}

@@

%% \pmb{ Definition.}
\begin{definition}
	A \textbf{ symbol} \(\mathcal{S}\) is defined as an object in \(\text{Sym}(\mathcal{C})\) which is a sub category of \(\mathcal{C}\). There exists a functor from \(\text{Sym}(\mathcal{C})\) to \(\text{Not}(\mathcal{C})\):

@@

	\[\epsilon :\alpha \equiv \beta\]
\end{definition}

@@

%% \pmb{ Definition.}
\begin{definition}
	A notation \(\mathcal{N}\) is called being \textbf{ inherited} from notation \(\mathcal{M}\) (or we say \(\mathcal{N}\) is\textbf{  a kind of} \(\mathcal{M}\)) when there exists such morphism between the two in \(\text{Not}(\mathcal{C})\):

@@

	It is obviously without any ambiguity that \(\forall \mathcal{M},\mathcal{N}\in \text{Not}(\mathcal{C}),\left|\text{Hom}_{\mathcal{C}}(\mathcal{M},\mathcal{N})\right|\in \{0,1\}\). Moreover, if \(\mathcal{N}\) is a kind of \(\mathcal{M}\) then \(\mathit{p}(\mathcal{N})\geq \mathit{p}(\mathcal{M})\). For simplicity, \(\mathcal{N}\) is inherited from \(\mathcal{M}\) can be annotated as \(\mathcal{N}\triangleleft |\mathcal{M}\).
\end{definition}

@@

%% \pmb{ Example.}
Using the structure provided by Bracket, Notation and Symbol to construct the example formula below, with meta category \(\mathcal{C}_1\).

@@

%% \pmb{ Definition.} 
\begin{definition}
	A micro-statement is a defined as an object in \(\text{Bra}(\mathcal{C})\) whose notation \(\mathcal{N}\) has \(\mathit{p}(\mathcal{N})=2\) and can be evaluated into a Boolean.

	It is essential to pay attention to that a bracket with 2-parameter notation is not necessarily a micro-statement. This conclusion can be illustrated via the example of \(\{(0,+),(1,x),(2,y)\}\) whose notation has two symbols as parameters but is not a micro-statement. The second restriction is more important, which is that a micro-statement must have the capacity to be evaluated into a Boolean value, that is, \(\text{true}\) or \(\text{false}\). What is notable, the \textbf{ evaluation} process is not declared inside the representation system, whose definition comes below. All micro-statement brackets forms the \textbf{ Micro-Statement }sub category of \(\text{Bra}(\mathcal{C})\) and is annotated as \(\text{Mic}(\mathcal{C})\).
\end{definition}

@@

%% \pmb{ Definition.}
\begin{definition}
	An evaluation is a morphism from \(\text{Mic}(\mathcal{C})\) to a Boolean algebra \(\mathcal{B}\) with the form below.

@@

	The Boolean value \(\mathit{e}\mathit{v}\mathit{a}\ell (\mathit{m})\in \{0,1\}\) is called the \textbf{ evaluation result} of micro-statement. If for bracket \(\mathit{m}\) exists a morphism to \(\mathcal{B}\) that satisfies the definition of evaluation, then we say that \(\mathit{m}\) is \textbf{ evaluatable}. That is, if it satisfies the first restriction of being a micro-statement as well, it is a micro-statement.
\end{definition}

@@

The discussion below calls the \(\text{Mic}(\mathcal{C})\) category the \textbf{ micro-statement pool}, or \textbf{ pool} for short. The morphisms inside the micro-statements pool are declared for representation of implication relationships. It is obvious and elementary that,

@@

%% \pmb{ Definition.}
\begin{definition}
	A \textbf{ derivation} is a set of ordered pairs of ordinals and categories in the form below.

@@

	For simplicity of expression, we use notation \(\mathcal{M}_i\) to represent the right pair element in $\mathcal{D}$ { }whose left companion is \(i\).
\end{definition}

@@

%% \pmb{ Definition.}
\begin{definition}
	A \textbf{ step of derivation} is a map existed on the derivation set \(\mathcal{D}\), mapping from a pair to another, whose ordinal increases by \(1\). This map is annotated using script word \(\mathit{s}\mathit{t}\mathit{e}\mathit{p}\). The form is shown below:

@@

	\[\mathcal{M}_{i+1}=\mathcal{F}_i\mathcal{M}_i\]
\end{definition}

@@

%% \pmb{ Definition.} 
\begin{definition}
	A derivation set is thought to be \textbf{ successful} when the condition below is satisfied when the condition below is true:

@@

	On the other hand, a derivation set is thought to be \textbf{ impossible} when there does not exist such a \(n\in [0,\omega )\) that makes the requirement set a subset of the object set of the targeted micro-statement pool.
\end{definition}

@@

%% \pmb{ Definition. }
\begin{definition}
	A \textbf{ reflection functor} \(\mathcal{K}\) is defined as an functor object in a functor category \(\mathcal{R}\mathit{e}\mathit{f}\), who maps between two micro-statement pools. Because of the Zermelo{'}s Well-Ordering Theorem we mentioned in the Preliminary section, \(\text{Ob}(\mathcal{R}\mathit{e}\mathit{f})\) can be put into well-order, with ordinal \(i\). All of the reflection functors forms a functor category \(\mathcal{Q}\), called the \textbf{ reflection knowledge base}, or for short the \textbf{ knowledge base}. The detailed explanation and description, including the utilization of and morphisms inside the knowledge base, will be discussed later in this section of the paper. We annotate each of the functor positioned at location \(i\) with \(\mathcal{K}_i\).

@@

	\[\sigma =T(\mathcal{K})_{\ell }\]
	\[\tau =T(\mathcal{K})_{\mathit{r}}\]
\end{definition}

@@

%% \pmb{ Definition.}
\begin{definition}
	The process of isomorphism inspection is declared as below. The stuff that the isomorphism inspection process manipulates is a micro-statement \(\mu \in \mathcal{M}_i\), a special evaluatable sort of bracket. The definition of bracket being isomorphic can be found in the second section. Explicitly, the inspection process is to construct a new set called the \textbf{ transformation source}, noted as \(\text{Ts}\) using the equation below.

	\[\text{Ts}\text{:=}\left\{t\in \mathcal{M}_i|t\simeq T(\mathcal{K})_{\ell }\right\}\]
\end{definition}

@@

%% \pmb{ Definition.}
\begin{definition}
	A \textbf{ transformation map} is a one-one map defined between the list of symbol and sub-brackets of the two brackets \(\alpha\) and \(\beta\) where,

@@

	\[\mathcal{M}_{i+1}=\mathcal{M}_i\cup \mathcal{M}'\]
\end{definition}

@@

%% \pmb{ Definition. }
\begin{definition}
The \textbf{ initial map }is the original state of knowledge base \(\mathcal{Q}\) when \(\mathcal{Q}\) is created. Initially, after the reflection functors are sorted, while discussions around this take place before, they forms a circular with connection of morphisms. That is, for \(N=|\text{Ob}(\mathcal{Q})|\),

@@

A morphism in this category means that if the reflection functor on its start is executed just now, then the target functor will be executed next time. That is, to be more specific, if a functor in \(\mathcal{Q}\) has no morphisms targeting it, then it will be never executed unless it is configured as the beginning functor (location \(0\)) manually. Moreover, if a functor has more than one morphisms starting from it, then we call this functor \textbf{ extroverted}. Otherwise, if a functor has more than one morphisms targeting it, it is \textbf{ introverted}. If one has only two morphisms connected, one in and one out, thus it is\textbf{  ordinary}. The process of determining the next functor of a extroverted functor will be discussed below.
\end{definition}

@@

%% \pmb{ Definition. }
\begin{definition}
	A recursive functor \(\mathcal{F}_i\) is a functor that applies to pool \(\mathcal{M}_i\) and evolves it into \(\mathcal{M}_{i+1}\). The process of determining which \(\mathcal{K}_w\) is \textbf{ selected} after former reflection functor \(\mathcal{K}_j\) generally works on the knowledge base \(\mathcal{Q}\), right starting from the initial map. If this is the first time for the recursive functor to execute, then \(\mathcal{K}_0\) is selected. If \(\mathcal{F}_i\) encounters with an introverted or ordinary functor \(\mathcal{K}_j\) then significantly,

@@

	It is easy to understand that for each reflection functor \(\mathcal{K}_a\) and \(\mathcal{K}_b\), the count of set \(\text{Hom}_{\mathcal{Q}}\left(\mathcal{K}_a,\mathcal{K}_b\right)\) indicates the \textbf{ weight} of \(\mathcal{K}_b\) to \(\mathcal{K}_a\), controlling the probability of \(\mathcal{K}_b\) to be selected when the former functor is \(\mathcal{K}_a\). The design of this process is inspired by the lottery scheduling algorithm I learned in Andrew S. Tanenbaum{'}s Operating Systems: Design and Implementation \cite{6} before.
\end{definition}

@@

%% \pmb{ Definition.}
\begin{definition}
	The process of knowledge reinforcement is done after a finishing a proof. The first step of this reinforcement is to add numbers of utilization of the corresponding morphism of copies of morphisms into the knowledge base, increasing the weight of connections between the reflection functors. When next time a proof is issued, the modified knowledge base is \textbf{ loaded} into instance and act as the modified initial situation.

	The second step of this sort of reinforcement is called \textbf{ reduction}, which is based on the Ebbinghaus{'}s forgetful curve{'}s numerical fit function. The exact form of the function expression can be found in the Preliminary section. Specifically, the number of morphisms is decreased following the forgetful equation, changing into the nearest integer number. To be more explicit, the Ebbinghaus-reduced decimal is stored separately from the knowledge base and the exact and accurate representation for this is omitted in the paper.
\end{definition}

A situation after some reinforcements may be the one demonstrated in the figure on the next page.

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}[commutative diagrams/every diagram]
		\node (K0) at (90:2.3cm) {$\mathcal{K}_0$};
		\node (K1) at (90+72:2cm) {$\mathcal{K}_1$};
		\node (K2) at (90+2*72:2cm) {$\mathcal{K}_2$};
		\node (K3) at (90+3*72:2cm) {$\mathcal{K}_3$};
		\node (Kn) at (90+4*72:2cm) {$\mathcal{K}_N$};

@@

		\path[commutative diagrams/.cd, every arrow, every label, dashed]
		(K3) edge node {$K_3$} (Kn)
		(Kn) edge node {} (K1)
		(Kn) edge node {$k_N$} (K0);
	\end{tikzpicture}
	\caption{An example map after several reinforcements.}
\end{figure}

Readers may notify that that \(\mathcal{K}_1\) has a morphism targeting \(\mathcal{K}_N\) and \(\mathcal{K}_N\) also has a morphism targeting \(\mathcal{K}_1\). This consequence is normal and natural following the evolution. Another possible issue is that after some recursions, there may exist some stuff whose weight is below the least acceptable numerical, that is, they are \textbf{totally forgotten}. Well, in such condition, they will be absolutely no recursion involving them. The only way to restore their activity is to reconfigure their parameter manually.

@@

Currently I have developed a computer program called sDefQed that implements the algorithm and it is open-sourced with BSD 3-Clause {``}New{''} or {``}Revised{''} License on GitHub. The source code of the latest version can be accessed at \cite{7} It should be noted that the version is very early and some aspects of the algorithm I presented in the paper is not implemented.

@@

\bibliographystyle{acm}
\bibliography{document}
\end{document}
